First and foremost, I would like to thank Tim Butler. 
Thanks for giving me the opportunity to perform the work, bringing me up to speed on the skills I needed for the work and always being there to offer advice. 
Allowing a mathematician to step up to the world of atmospheric chemistry speaks very highly of you.
I also appreciate the criticism which helped me improve my work, your sense of humour and that we make a good basis for a successful pub quiz team!

Secondly, I would like to thank Mark Lawrence and the IASS Potsdam for scientific and financial support of the project.
Working at the IASS has not only helped to develop my disciplinary knowledge of atmospheric chemistry but also to keep in mind that scientific excellence alone is not the sole basis of societal transformation.
The interdisciplary and transdisciplinary approaches are needed to complement disciplinary work, I could not have truely understood this without working at the IASS Potsdam.

I thank Peter Builtjes for the collaboration and support during the project.
Your pleasant comments and input during the many PAC meetings is greatly appreciated.

Thanks also goes to all my colleagues, past and present, at the IASS Potsdam.
All the discussions, translating, running breaks, cake breaks and coffee breaks helped me throughout this time!

Last but not least, I must thank Nadja Menz: you have sat through so many trial presentations, proofread texts and supplied an adequate amount of coffee and baked goodies to fuel me through this work. 
For your unwaivering support that takes on many forms - thanks!
