This chapter outlines the main findings in each scientific paper published as part of this thesis.
These publications addressed the research questions framed in Sect.~\ref{s:research_questions} and are found in Chaps.~\ref{c:paper_1}--\ref{c:paper_3}.

\singlespacing
\section[Paper I]{Paper I: A comparison of chemical mechanisms using tagged ozone production potential (TOPP) analysis} \label{s:chemical_mechanism_results}
\onehalfspacing

Published: \bibentry{Coates:2015}.
\vspace{5mm}

The first paper presents a box modelling study where the effects on ozone production from VOC degradation chemistry in reduced chemical mechanisms (Table~\ref{t:mechanisms}) was compared to the detailed MCM chemical mechanisms.
Other chemical mechanism comparison studies noted differences in ozone levels between chemical mechanisms, however these studies did not deduce the root causes for these differences.
%The aims of this study were to determine the differences in ozone produced from different VOC by the different chemical mechanisms and the most important processes for simulating ozone production.
This chemical mechanism comparison used the tagging approach described in Sect.~\ref{s:tagging} to give insights into how the simplified representation of VOC degradation by chemical mechanisms influenced ozone production.

The ozone production from the degradation of VOCs typical of urban environments were compared between the different chemical mechanisms.
The box model simulated maximum ozone production (VOC-and-\ce{NO_x}-sensitive) regime by emitting the amount of NO required to balance the source of radicals at each time step.
As described in Sect.~\ref{s:tagging}, the tagging approach used the production of \ce{O_x} as a proxy for ozone production.

The simulated ozone mixing ratios using reduced chemical mechanisms were generally lower than the ozone mixing ratios using the reference MCM chemical mechanisms on the first two days of simulations.
Only the CRI~v2 and RADM2 produced higher ozone mixing ratios than the MCM chemical mechanisms.
Higher ozone mixing ratios using CRI~v2 than the MCM were obtained during the development of the CRI~v2.
In RADM2, a lower yield of ketones from the degradation of HC3 (representing less-reactive VOC such as alkanes and alcohols) compared to the MCM led to higher ozone mixing ratios with RADM2.

The VOC degradation described in CRI~v2, a lumped-intermediate chemical mechanism, produced the most similar amounts of \ce{O_x} to the MCM~v3.2 for each VOC.
On the other hand, the degradation of VOC in all other reduced chemical mechanisms led to differences in \ce{O_x} production with the largest differences occuring after the first day of simulations.
The degradation of aromatic VOC in the reduced chemical mechanisms led to the largest differences in \ce{O_x} production from the MCM~v3.2.

Many VOC are broken down into smaller-sized degradation products faster on the first day in reduced chemical mechanisms than the MCM~v3.2.
The faster breakdown of VOC leads to lower amounts of larger-sized degradation products that can further degrade and produce \ce{O_x} in the reduced chemical mechanisms.
Thus, many VOC in reduced chemical mechanisms produce a lower maximum of \ce{O_x} than the MCM~v3.2 resulting in lower \ce{O3} mixing ratios from the reduced chemical mechanisms compared to the MCM~v3.2.

Reactive VOC, such as alkenes and aromatic VOC, produce maximum \ce{O_x} on the first day of the simulations.
Alkenes produce similar amounts of \ce{O_x} on the first day between chemical mechanisms; differences in \ce{O_x} production arise when mechanism species are used to represent individual VOC.
Large inter-mechanism differences in \ce{O_x} production result from the degradation of aromatic VOC on the first day due to the faster break down of the mechanism species representing aromatic VOC in reduced chemical mechanisms.
The less-reactive alkanes produce maximum \ce{O_x} on the second day of simulations and this maximum is lower in each reduced chemical mechanism than the MCM~v3.2 due to the faster break down of alkanes into smaller sized degradation products on the first day.

\singlespacing
\section[Paper II]{Paper II: Variation of the NMVOC Speciation in the Solvent Sector and the Sensitivity of Modelled Tropospheric Ozone} \label{s:EI_results}
\onehalfspacing

Published: \bibentry{vonSchneidemesser:2016}.
\vspace{5mm}

The second publication compared the ozone levels produced when using different emission inventories of NMVOC emissions for the solvent sector within a box model.
Different chemical mechanisms (MCM~v3.2, MOZART-4 and RADM2) were used to ascertain whether the representation of tropospheric chemistry affected the differences in ozone production when using the different emission inventories.

Emission inventories (EIs) are a critical model input but also a major source of uncertainty in modelling studies.
For example, the speciations of EIs in many locations are not reflected by ambient measurements, EIs may not adequately reflect the temporal nature of emissions and many EIs may be outdated.
Before taking upon the huge task of updating EIs addressing these issues, a scoping study looking at the sensitivity of ozone production when changing the model input from was performed in this study.

The experimental setup considered emissions from the solvent sector as this sector has the largest contribution to NMVOC. 
Model simulations used \ce{NO_x} conditions simulating VOC-and-\ce{NO_x}-sensitive conditions thus looking at the differences in maximum ozone production when using the emission inventories for the solvent sector in Table~\ref{t:solvent_speciations}.
Furthermore, simulations were performed using different chemical mechanisms (MCM~v3.2, MOZART-4 and RADM2) comparing the differences with different representations of VOC degradation chemistry.
Simulations using the tagging chemical mechanisms in Sect.~\ref{s:chemical_mechanism_results} were performed allowing allocation of \ce{O_x} production to the emitted NMVOC specified by each EI.

A maximum difference in ozone mixing ratios ranging between $11$~ppb and $15$~ppbv when using the different EIs was obtained from the box model simulations using each chemical mechanism.
When using the same EI speciation, a maximum difference of $6.7$~ppbv in ozone mixing ratios was determined between simulations with different chemical mechanisms.
Thus both the choice of chemical mechanism and EI influenced the amount of ozone produced.

Further simulations using emissions from all other non-solvent sectors while varying the emissions from the solvent sector produced a lower maximum difference in ozone mixing ratio ($6$--$9$~ppbv) for each chemical mechanism.
When further including emissions from biogenic sources reduced the maximum differences in ozone mixing ratios even further ($5$--$8$~ppbv) with each chemical mechanism.

Reactive VOC, such as alkenes and aromatic VOC, had the highest contribution to \ce{O_x} production on the first day.
While less-reactive VOC, such as alkanes and oxygenated VOC, contributed the most to the cumulative \ce{O_x} production after seven days.

EIs specifying more emissions of alkanes produced more \ce{O_x} than EIs specifying larger emissions from oxygenated NMVOC.
A positive correlation between \ce{O_x} production and the specification of alkane species by the EIs was determined while a negative correlation was determined between cumulative \ce{O_x} production and specification of oxygenated species by the EIs.
No correlation was found between the specification of aromatic species by EIs and \ce{O_x} production and not all EIs specify alkene emissions thus no correlation was made between alkene emissions and \ce{O_x} production.

\singlespacing
\section[Paper III]{Paper III: The Influence of Temperature on Ozone Production under varying \ce{NO_x} Conditions -- a modelling study} \label{s:T-O3_results}
\onehalfspacing

Published: \bibentry{Coates:2016}.
\vspace{5mm}

The final study of this thesis looked at the ozone-temperature relationship with different \ce{NO_x} conditions simulated by a box model.
A non-linear relationship between ozone production with temperature and \ce{NO_x} conditions has been noted using an analytical model constrained to observational measurements but not yet reproduced in a modelling study.
Temperature increases ozone production through increasing NMVOC emissions from biogenic sources and by increasing the rates of chemical reactions.
Modelling studies have as yet not quantified which of these effects is more important for ozone production.
The study aimed to determine whether temperature-dependent increases in reaction rates or isoprene emissions were more important for ozone production on the urban scale and whether the non-linear relationship of ozone with temperature and \ce{NO_x} was reproduced using different chemical mechanisms.

Box model simulations were performed using NMVOC emissions representative of central Europe, first using a temperature-independent source of isoprene emissions followed by simulations using the temperature-dependent source of isoprene emissions described using the MEGAN2.1 algorithm.
The choice of chemical mechanism may also influence the relationship of ozone on temperature, thus all simulations were repeated using the MCM~v3.2, CRI~v2, MOZART-4, RADM2 and CB05 chemical mechanisms.
Model simulations included vertical mixing to the free troposphere and were performed by systematically varying the temperature and NO emissions at each temperature (Sect.~\ref{s:initial_conditions}).
The tagged chemical mechanisms could not be used in this study as the \ce{NO_x} conditions gave rise to simulations with \ce{NO_x}-saturated conditions where using \ce{O_x} production as a proxy for ozone production is not valid (Sect.~\ref{s:tagging}).

A non-linear relationship of ozone with temperature and \ce{NO_x} emissions was produced using each chemical mechanism. 
This non-linear relationship was similar to that previously reported from observational studies.  
In each chemical mechanism, the absolute increase in ozone with temperature was greater for temperature-dependent chemistry than the increase ozone with temperature due to isoprene emissions.
The largest increases in ozone mixing ratios were obtained in High-\ce{NO_x} conditions and the lowest increase in ozone mixing ratios was achieved using Low-\ce{NO_x} conditions.

The net increase in the production of \ce{O_x} normalised by the loss rate of emitted VOCs with temperature was caused by the decrease in ozone deposition with temperature.
Furthermore, the \ce{O_x} production was constant with temperature showing that the production of \ce{O_x} with temperature was controlled by the loss rate of VOCs.
The increased loss rate of VOCs with temperature was mainly due to the increase of OH with temperature. 
The increase in OH with temperature is coupled to the increase of ozone with temperature showing the strong coupling of ozone with OH.

The box model results were also compared to observational data and output from the 3-D model WRF-Chem.
The rate of increase of ozone with temperature from the box model was about half the rate of increase of ozone with temperature using observational and WRF-Chem output.
Observational data and the output of 3-D models such as WRF-Chem include additional effects of temperature on ozone, such as stagnant conditions, where low wind speeds lead to the accumulation of oxidants promoting ozone production.

Model simulations were performed without mixing to approximate stagnant conditions and in these model simulations the increase in ozone with temperature was faster than the model simulations including mixing.
The differences in the rate of increase of ozone with temperature between mixing simulations and chemical mechanisms indicated a higher sensitivity to mixing than the choice of chemical mechanism.
